%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{:#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeProject}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubsub}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\href{#5}{#1}}&#2 \\
      %\textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSub}[4]{
  
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \text{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{}{\Large Xixian Yang}} & Email : \href{}{xyang180@asu.edu}\\
  \href{}{711 N Evergreen Rd. Mesa, AZ, 85201} & Mobile : +1-480-452-7921 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arizona State University}{Tempe, U.S.}
      {B.S. Computer Science; GPA: 3.74 }{Aug 2019 - Exp. May 2023}
    \vspace{+1pt}
     
    \textbf{Selected Coursework:} {\small Data Structure and Algorithms, Distributed Software Development, Software Engineering, Operating Systems, Assembly Language Programming, Theoretical Computer Science, Database Management}    
  \resumeSubHeadingListEnd
 
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {MOLBASE Chemical Database}{Shanghai, China}
      {Software Engineer Intern}{June 2021 - Aug 2021}
        \resumeItemListStart
        \resumeProject{}
           {MOLBASE is a data-driven chemical e-commerce integrated service platform, and is also the largest platform in China}
        \resumeProject{}
           {Developed the API of Qixinbao which is a Chinese enterprise information query tool has \textbf{20000 enterprise users}. 
          website by \textbf{Java} and \textbf{MySQL}.}
        \resumeProject{}
            {Build the API using \textbf{Java Spring}, which is used by business users to open an online store on the Molbase platform.}
        \resumeProject{}
            {Obtained data from API document.}

        \resumeProject{}
            {Provide an automated and efficient auditing service for over \textbf{2000 companies}.}
        \resumeProject{}{Maintained the Molbase website. Fixed bugs, such as product synchronization errors in database (\textbf{MySQL}), store products displayed incorrectly and membership expiration problems, etc}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
     \resumeSubheading
      {\href{https://github.com/XixianWasTaken/Golang-Based-Bookings-Application}{Hotel Booking App}}{}
      {Go, Javascript, PostgreSQL, JSON, Unit test, Git}{}
      \resumeItemListStart
      \resumeProject{}
          {A hotel booking system allows users to search for rooms by date and reserve room, and allows hotel manager to manage reservations.}
        \resumeProject{}
          {Implemented a real-time database using \textbf{PostgreSQL} to store the user data, and build the backend using \textbf{Go}.}
        \resumeProject{}
          {Implemented a interactive front-end UI using \textbf{Javscript}, which allows user to search and reserve avilable rooms.}
        \resumeProject{}
          {Using \textbf{PGX} connect from database and backend, \textbf{Chi} as router connect, \textbf{Git} as a version control tool and using \textbf{Go-testing} as unit testing}
        
      \resumeItemListEnd
      \vspace{+3pt}
      \resumeSubheading
      {\href{https://github.com/XixianWasTaken/Kickstarter}{Web3 Kickstarter}}{}
      {React, JavaScript, Solidity, Web3.js, Blockchain}{}
      \resumeItemListStart
        \resumeProject{}
        {A kickstater web application written in \textbf{Solidity} and deployed on the \textbf{Rinkbey} \textbf{Ethereum} network}
        \resumeProject{}
        {Using \textbf{React} as front-end development, \textbf{Web3.js} interacts with Ethereum addresses and networks.}
        \resumeProject{}{Users can use their \textbf{Metamask} wallets to interact with this smart contract to initiate project or participate in projects.}
        \resumeProject{}{Every project is a community. Every user in this community can vote for next step of project or donate ETH to the project}
      \resumeItemListEnd
   \vspace{+3pt}
      \resumeSubheading
      {\href{https://github.com/XixianWasTaken/CSE360}{Automation System For Pediatric Doctor’s Office}}{}
      {Java, JavaFX, MySQL, Junit, Git}{}
      \resumeItemListStart
        \resumeProject{}
          {It is a software that allows real-time interaction between doctors, nurses and patients}.
           \resumeProject{}
                {Using \textbf{JavaFX} for software GUI to allowed user interaction.}
            \resumeProject{}
                {Designed a real-time \textbf{MySQL} database and using \textbf{Junit} as a unit testing to ensure software robustness and security.}
            \resumeProject{}
                {Using \textbf{JDBC} to connect Java and Database.}
            \resumeProject{}
                {Using \textbf{Git} and \textbf{Github} as version control tools and to coordinate progress among group members}
          \resumeProject{}
            {I am the team leader in this project and coordinate the progress of each team member.} 
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{\textbf{Programming Languages}{: Java, Go, Python, Jupyter, C/C++, JavaScript, HTML, CSS, SQL, Solidity}}
     \vspace{-5pt}
    \item{\textbf{Framework and Tools:}{Web (React, Bootstrap, Web3.js, Node.js, Java Spring Boot), Cloud (AWS), Database (MySQL, JDBC), Misc (Git, Linux, Docker)}}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
